---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# runi

<!-- badges: start -->
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R-CMD-check](https://github.com/vgherard/runi/workflows/R-CMD-check/badge.svg)](https://github.com/vgherard/runi/actions)
[![Codecov test coverage](https://codecov.io/gh/vgherard/runi/branch/master/graph/badge.svg)](https://codecov.io/gh/vgherard/runi?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/runi)](https://CRAN.R-project.org/package=runi)
[![R-universe status](https://vgherard.r-universe.dev/badges/runi)](https://vgherard.r-universe.dev/)
<!-- badges: end -->

`{runi}` provides a client for R-universe APIs associated to R-universes. From the [R-universe project page](https://ropensci.org/r-universe/):

> The package server provides REST APIs for managing package submissions and querying information about individual packages as well as on the repository level. These data can be accessed programmatically or displayed in a front-end dashboard.

## Installation

You can install the development version of `runi` using

``` r
# install.packages("devtools")
devtools::install_github("vgherard/runi")
```


## Example

```{r example}
df <- runi::runi_stats_descriptions("vgherard")
df[, c("Package", "Title", "Version")]
```
